---
title: "Lab2"
output: html_document
---

## Setup

Before anything is started, we are going to load the libraries for the biostatistics/Clinical trials data set

```{r}
library(survival)
data(pbc)
```

## Non trivial analysis

Now, we have our data points and we want to do something with it. Lets focus on cholestrol. Lets see cholestrols mean, low, medium, and high values

```{r}
truechol <- pbc$chol[!is.na(pbc$chol)]
summary(truechol)
```

Now, we are to add the different levels of cholestrol based on risk.

```{r}
library(dplyr)
chollevels <- as.data.frame(truechol)
Chollevels <- chollevels %>%
  mutate(risklevels = case_when(
    truechol < 200 ~ "Low risk",
    truechol < 300 ~ "Medium risk",
    truechol < 400 ~ "High risk",
    truechol > 500~ "Severe risk",
  ))

```

## Visualization

Here, we will visualize some data regarding the chol levels

```{r}
countsChol <- table(Chollevels)
barplot(countsChol,
        main = "Number of patients per cholestrol risk group",
        xlab= "Category of risk level",
        ylab= "Amount of patients",
        col = "green")
```
